Modeling tabular icebergs coupled to an ocean model

### 2017-02-28 JAMES_iceberg_only.tex
Adding JAMES formatted iceberg_only manuscript. Also, a new Figure 1 has been adde which shows a schematic of the hexagonal icebergs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUtmpl.tex: this template file is for articles formatted with LaTeX2e,
% Modified July 2011
%
% This template includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements.
%
% PLEASE DO NOT USE YOUR OWN MACROS
% DO NOT USE \newcommand, \defcommand, or \renewcommand.
%
% FOR FIGURES, DO NOT USE \psfrag or \subfigure.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% All questions should be e-mailed to latex@agu.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Step 1: Set the \documentclass
%
% There are two options for article format: two column (default)
% and draft.
%
% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
% The draft option produces double spaced output.
%
% Choose the journal abbreviation for the journal you are
% submitting to:

% jgrga JOURNAL OF GEOPHYSICAL RESEARCH
% gbc   GLOBAL BIOCHEMICAL CYCLES
% grl   GEOPHYSICAL RESEARCH LETTERS
% pal   PALEOCEANOGRAPHY
% ras   RADIO SCIENCE
% rog   REVIEWS OF GEOPHYSICS
% tec   TECTONICS
% wrr   WATER RESOURCES RESEARCH
% gc    GEOCHEMISTRY, GEOPHYSICS, GEOSYSTEMS
% sw    SPACE WEATHER

% (If you are submitting to a journal other than jgrga,
% substitute the initials of the journal for "jgrga" below.)

\documentclass[draft,jgrga]{AGUTeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OPTIONAL:
% To produce a two-columned version:
% \documentclass[grl]{AGUTeX}

% Two-columned format can be used to estimate the number of pages
% for the final published PDF.

% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OPTIONAL:
% To create numbered lines:

% If you don't already have lineno.sty, you can download it from
% http://www.ctan.org/tex-archive/macros/latex/contrib/ednotes/
% (or search the internet for lineno.sty ctan), available at TeX
%Archive Network (CTAN).
% Take care that you always use the latest version.

% To activate the commands, uncomment \usepackage{lineno}
% and \linenumbers*[1]command, below:
% To activate the commands, uncomment \usepackage{lineno}
% and \linenumbers*[1]command, below:
\usepackage{amsmath, amsthm, amssymb}
 \usepackage{lineno}
 \linenumbers*[1]

 %\usepackage{lineno}
 %\linenumbers*[1]

%  To add line numbers to lines with equations:

%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figures and Tables
%
% When submitting articles through the GEMS system:
% COMMENT OUT ANY COMMANDS THAT INCLUDE GRAPHICS.
% (See FIGURES section near the end of the file.)
%
% DO NOT USE \psfrag or \subfigure commands.
%
%  Figures and tables should be placed AT THE END OF THE ARTICLE,
%  after the references.
%
%  Uncomment the following command to include .eps files
%  (comment out this line for draft format):
 \usepackage{graphicx}
 \usepackage{ulem}
\usepackage{color}
  %
%  Uncomment the following command to allow illustrations to print
%   when using Draft:
  \setkeys{Gin}{draft=false}
%
% Substitute one of the following for [dvips] above
% if you are using a different driver program and want to
% proof your illustrations on your machine:
%
% [xdvi], [dvipdf], [dvipsone], [dviwindo], [emtex], [dviwin],
% [pctexps],  [pctexwin],  [pctexhp],  [pctex32], [truetex], [tcidvi],
% [oztex], [textures]
%
% See how to enter figures and tables at the end of the article, after
% references.
%
%% ------------------------------------------------------------------------ %%
%
%  ENTER PREAMBLE
%
%% ------------------------------------------------------------------------ %%

% Author names in capital letters:
\authorrunninghead{STERN ET AL.}

% Shorter version of title entered in capital letters:
%\titlerunninghead{Remote and local affects of large Antarctic icebergs}
%\titlerunninghead{Effects of iceberg calving size}
\titlerunninghead{Modeling tabular icebergs}

% Author mailing address: please repeat this command for
% each author and alphabetize authors:

\authoraddr{A. A. Stern, Geophysical Fluid Dynamics Laboratory, Princeton University}

\authoraddr{A. Adcroft, Geophysical Fluid Dynamics Laboratory, Princeton University}

\authoraddr{O. Sergienko, Geophysical Fluid Dynamics Laboratory, Princeton University}

\authoraddr{G. Marques, Geophysical Fluid Dynamics Laboratory, Princeton University}

\authoraddr{R. Hallberg, Geophysical Fluid Dynamics Laboratory, Princeton University}

%
\begin{document}

%% ------------------------------------------------------------------------ %%
%
%  TITLE
%
%% ------------------------------------------------------------------------ %%

%\title{Remote and local effects of large Antarctic icebergs}
%OR\\
%\title{The effect of calving-size distribution on sea-ice formation around Antarctica}
\title{Modeling tabular icebergs coupled to an ocean model}
%\title{The effects of iceberg calving-size distribution in a global climate model}
% e.g., \title{Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$}
%

@@

%Use \author{\altaffilmark{}} and \altaffiltext{}

 %\altaffilmark will produce footnote;
% matching \altaffiltext will appear at bottom of page.

 \authors{A.A. Stern,\altaffilmark{1} , A. Adcroft\altaffilmark{1}
   and O. Sergienko \altaffilmark{1} , G. Marques\altaffilmark{1}, R. Hallberg\altaffilmark{1}}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
%% ------------------------------------------------------------------------ %%

% >> Do NOT include any \begin...\end commands within
% >> the body of the abstract.

\begin{abstract}
The calving of giant icebergs from the Antarctic ice shelves accounts for approximately half of Antarctic ice-shelf decay. After calving, these tabular icebergs drift across large distances, altering regional ocean circulation, bottom-water formation, sea-ice production and biological primary productivity in the icebergs' vicinity.
However, despite their importance, the current generation of numerical models is unable to represent giant tabular icebergs in a physically realistic way.
In this study we develop a novel framework to model giant tabular icebergs submerged in the ocean. In this framework, tabular icebergs are constructed out of Lagrangian elements that drift in the ocean, and are held together by numerical bonds.
By breaking these bonds, a tabular iceberg can be made to split into smaller pieces, or to break away from an ice shelf.
We describe the Lagrangian tabular-iceberg model and discuss a number of the technical elements involved in its development. 
We demonstrate the capabilities of the model by modeling a tabular iceberg drifting away an idealized ice shelf.
\end{abstract}
%% ------------------------------------------------------------------------ %%
%
%  BEGIN ARTICLE
%
%% ------------------------------------------------------------------------ %%
% The body of the article must start with a \begin{article} command
%
\clearpage
\vspace{10mm}
\textbf{Key Points:}\\

% \end{article} must follow the references section, before the figures
%  and tables.
\begin{article}
%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%
\section{Introduction}
%\subsection{Key points for writing introduction}
%
%1) Physical processes that affect the ocean circulation around Antarctica (involving ice shelf cavities /tabular icebergs). 
%
%2) Why is it important that we are about to model these regions correctly, and tabular icebergs?
%
%3) What are the significant efforts that have been made thus far towards correctly modeling ice shelf cavities / Antarctic fresh water fluxes.
%
%4) What is missing - and what we intend to add
%
%5) Similar things which have been done in the past (if there are any)
%
%6) Short summary and paper description.
%
%\subsection{Introduction}

@@

 \subsection{Model configuration}
We initialized our simulation using the experimental setup created for the Marine Ice Ocean Modeling Inter-comparion Project (MISOMIP) \citep{Asay-Davis2016}.
The configuration consists of an idealized ice shelf in a rectangular domain. The domain is $L_{x}=80$km wide and $L_{y}=480$km long, and contains an ice shelf which is grounded on the south side of the domain and has an ice front at y=650 km. The ice thickness and bottom topography of this setup are shown in Figure \ref{fig:ISOMIP_mass_and_topog}a and \ref{fig:ISOMIP_mass_and_topog}b respectively, with the grounding line position drawn in for reference. The configuration is the same as that of the Ocean0 setup in the MISOMIP, with a few minor changes to the ice-shelf geometry (see Appendix D for details).
% (see supplementary materials for details).
%
%with three changes made:
%\begin{enumerate}
%\item The `calving criteria' used in the MISOMIP study (which states that all points in the ice shelf with thickness less than 100m are set to zero thickness) has not been used.
%\item The ice shelf has been thickened on the flanks of the domain, so that the latitude of the grounding line increases away from the center of the ice shelf.
%\item The ice shelf is configured to be symmetric about its meridional center line ($x=\frac{L_{x}}{2}$). This was achieved by using the average of the left and right flanks of the ice-shelf thickness. 
%\end{enumerate}
%These three changes were made in order to make the circulation beneath the ice shelf easier to interpret.

@@

\section{Appendix D}
The experiment configuration used to initialize the calving tabular iceberg simulation (in this study) is the same as that of the Ocean0 setup in the MISOMIP, with the following three changes made:
\begin{enumerate}
\item The `calving criteria' used in the MISOMIP study (which states that all points in the ice shelf with thickness less than 100m are set to zero thickness) has not been used.
\item The ice shelf has been thickened on the flanks of the domain, so that the latitude of the grounding line increases away from the center of the ice shelf.
\item The ice shelf is configured to be symmetric about its meridional center line ($x=\frac{L_{x}}{2}$). This was achieved by using the average of the left and right flanks of the ice-shelf thickness. 
\end{enumerate}
These three changes were made in order to make the circulation beneath the ice shelf easier to interpret.

@@

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_spread_area.png}
\caption{ {Snapshots of the fraction of ice cover in the LTIM tabular iceberg calving simulation. Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving. The dashed line in panel (c) shows the location of the vertical transects shown in Figures \ref{fig:Velocity_section_Collapse} and \ref{fig:Temperature_section_Collapse}}.}
\end{center}
\label{fig:Spread_area}
\end{figure}
 \clearpage

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/hex_intersecting_rectangles}
\caption{ {(a) Hexagonal elements are initialized in a staggered lattice as shown. Adjacent elements are bonded together. The element bonds (plotted in pink) form equilateral triangles which give the larger structure rigidity. The black circles show the circular element shape used in element interactions, and are inscribed inside the hexagonal shape used for mass-spreading. (b) Intersection of a hexagonal element and the ocean grid. The colors indicate the fraction of the hexagon that lies in each grid cell. These fractions are used as weights to spread LTIM properties to the ocean grid (see text for more details).}}
\end{center}
\label{fig:Hex_intersections}
\end{figure}
 \clearpage

@@

@@

>>>>

%% 11/23/2015
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUJournalTemplate.tex: this template file is for articles formatted with LaTeX
%
% This file includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements. 
%
% You may copy this file and give it your
% article name, and enter your text.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PLEASE DO NOT USE YOUR OWN MACROS
% DO NOT USE \newcommand, \renewcommand, or \def, etc.
%
% FOR FIGURES, DO NOT USE \psfrag or \subfigure.
% DO NOT USE \psfrag or \subfigure commands.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Step 1: Set the \documentclass
%
% There are two options for article format:
%
% 1) PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
% The draft option produces double spaced output.
% 
% 2) numberline will give you line numbers.

%% To submit your paper:
\documentclass[draft,linenumbers]{agujournal}
\draftfalse

%% For final version.
% \documentclass{agujournal}

% Now, type in the journal name: \journalname{<Journal Name>}

% ie, \journalname{Journal of Geophysical Research}
%% Choose from this list of Journals:
%
% JGR-Atmospheres
% JGR-Biogeosciences
% JGR-Earth Surface
% JGR-Oceans
% JGR-Planets
% JGR-Solid Earth
% JGR-Space Physics
% Global Biochemical Cycles
% Geophysical Research Letters
% Paleoceanography
% Radio Science
% Reviews of Geophysics
% Tectonics
% Space Weather
% Water Resource Research
% Geochemistry, Geophysics, Geosystems
% Journal of Advances in Modeling Earth Systems (JAMES)
% Earth's Future
% Earth and Space Science
%
%

\journalname{Journal of Advances in Modeling Earth Systems (JAMES)}

\begin{document}

%% ------------------------------------------------------------------------ %%
%  Title
% 
% (A title should be specific, informative, and brief. Use
% abbreviations only if they are defined in the abstract. Titles that
% start with general keywords then specific terms are optimized in
% searches)
%
%% ------------------------------------------------------------------------ %%

% Example: \title{This is a test title}

\title{Modeling tabular icebergs coupled to an ocean model}

@@

% Authors are individuals who have significantly contributed to the
% research and preparation of the article. Group authors are allowed, if
% each author in the group is separately identified in an appendix.)

% List authors by first name or initial followed by last name and
% separated by commas. Use \affil{} to number affiliations, and
% \thanks{} for author notes.  
% Additional author notes should be indicated with \thanks{} (for
% example, for current addresses).

% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
% Author\affil{3,4}\thanks{Also funded by Monsanto.}}

\authors{A. A. Stern\affil{1}, A. Adcroft\affil{1}, O. Sergienko\affil{1}, G. Marques\affil{1}, R. Hallberg\affil{1}}

 \affiliation{1}{Geophysical Fluid Dynamics Laboratory, Princeton University}
% \affiliation{2}{Second Affiliation}
% \affiliation{3}{Third Affiliation}
% \affiliation{4}{Fourth Affiliation}

\affiliation{1}{201 Forrestal Rd, Princeton, NJ 08540, USA}
%(repeat as many times as is necessary)

%% Corresponding Author:
% Corresponding author mailing address and e-mail address:

% (include name and email addresses of the corresponding author.  More
% than one corresponding author is allowed in this LaTeX file and for
% publication; but only one corresponding author is allowed in our
% editorial system.)

% Example: \correspondingauthor{First and Last Name}{email@address.edu}

\correspondingauthor{Alon Stern}{sternalon@gmail.com}

%% Keypoints, final entry on title page.

% Example: 
% \begin{keypoints}
% \item	List up to three key points (at least one is required)
% \item	Key Points summarize the main points and conclusions of the article
% \item	Each must be 100 characters or less with no special characters or punctuation 
% \end{keypoints}

%  List up to three key points (at least one is required)
%  Key Points summarize the main points and conclusions of the article
%  Each must be 100 characters or less with no special characters or punctuation

\begin{keypoints}
\item = enter point 1 here = 
\item = enter point 2 here = 
\item = enter point 3 here = 
\end{keypoints}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
% A good abstract will begin with a short description of the problem
% being addressed, briefly describe the new data or analyses, then
% briefly states the main conclusion(s) and how they are supported and
% uncertainties. 
%% ------------------------------------------------------------------------ %%

%% \begin{abstract} starts the second page

\begin{abstract}
The calving of giant icebergs from the Antarctic ice shelves accounts for approximately half of Antarctic ice-shelf decay. After calving, these tabular icebergs drift across large distances, altering regional ocean circulation, bottom-water formation, sea-ice production and biological primary productivity in the icebergs' vicinity.
However, despite their importance, the current generation of numerical models is unable to represent giant tabular icebergs in a physically realistic way.
In this study we develop a novel framework to model giant tabular icebergs submerged in the ocean. In this framework, tabular icebergs are constructed out of Lagrangian elements that drift in the ocean, and are held together by numerical bonds.
By breaking these bonds, a tabular iceberg can be made to split into smaller pieces, or to break away from an ice shelf.
We describe the Lagrangian tabular-iceberg model and discuss a number of the technical elements involved in its development. 
We demonstrate the capabilities of the model by modeling a tabular iceberg drifting away an idealized ice shelf.
\end{abstract}

%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%

%%% Suggested section heads:
% \section{Introduction}
% 
% The main text should start with an introduction. Except for short
% manuscripts (such as comments and replies), the text should be divided
% into sections, each with its own heading.

% Headings should be sentence fragments and do not begin with a
% lowercase letter or number. Examples of good headings are:

% \section{Materials and Methods}
% Here is text on Materials and Methods.
%
% \subsection{A descriptive heading about methods}
% More about Methods.
% 
% \section{Data} (Or section title might be a descriptive heading about data)
% 
% \section{Results} (Or section title might be a descriptive heading about the
% results)
% 
% \section{Conclusions}

\section{Introduction}
%\subsection{Key points for writing introduction}
%
%1) Physical processes that affect the ocean circulation around Antarctica (involving ice shelf cavities /tabular icebergs). 
%
%2) Why is it important that we are about to model these regions correctly, and tabular icebergs?
%
%3) What are the significant efforts that have been made thus far towards correctly modeling ice shelf cavities / Antarctic fresh water fluxes.
%
%4) What is missing - and what we intend to add
%
%5) Similar things which have been done in the past (if there are any)
%
%6) Short summary and paper description.
%
%\subsection{Introduction}

@@

 \subsection{Model configuration}
We initialized our simulation using the experimental setup created for the Marine Ice Ocean Modeling Inter-comparion Project (MISOMIP) \citep{Asay-Davis2016}.
The configuration consists of an idealized ice shelf in a rectangular domain. The domain is $L_{x}=80$km wide and $L_{y}=480$km long, and contains an ice shelf which is grounded on the south side of the domain and has an ice front at y=650 km. The ice thickness and bottom topography of this setup are shown in Figure \ref{fig:ISOMIP_mass_and_topog}a and \ref{fig:ISOMIP_mass_and_topog}b respectively, with the grounding line position drawn in for reference. The configuration is the same as that of the Ocean0 setup in the MISOMIP, with a few minor changes to the ice-shelf geometry (see Supplementary Material for details).
% (see supplementary materials for details).
%
%with three changes made:
%\begin{enumerate}
%\item The `calving criteria' used in the MISOMIP study (which states that all points in the ice shelf with thickness less than 100m are set to zero thickness) has not been used.
%\item The ice shelf has been thickened on the flanks of the domain, so that the latitude of the grounding line increases away from the center of the ice shelf.
%\item The ice shelf is configured to be symmetric about its meridional center line ($x=\frac{L_{x}}{2}$). This was achieved by using the average of the left and right flanks of the ice-shelf thickness. 
%\end{enumerate}
%These three changes were made in order to make the circulation beneath the ice shelf easier to interpret.

@@

@@

\acknowledgments
 = enter acknowledgments here =

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/PIIB_with_hexagons.png}
\caption{Schematic showing how Lagrangian elements are used when modeling tabular icebergs. Lagrangian elements (blue dots) are initialized in a staggered lattice covering the surface area of the iceberg. For purposed of mass aggregation, the ice elements are assumed to have hexagonal shape (grey hexagons). For purposed of element interactions, the ice elements are assumed to be circular (black circles). Elements are initially bonded to adjacent elements using numerical bonds (dashed white lines). These numerical bonds form equilateral triangles which give the shape rigidity. The inset panel shows a schematic of the intersection of a hexagonal element and the ocean grid. The colors indicate the fraction of the hexagon that lies in each grid cell. These fractions are used as weights to spread LTIM properties to the ocean grid (see text for more details) The background photo in the larger schematic is an areal photograph of iceberg PIIB (Area= 42 $\textrm{km}^{2}$) taken in Baffin Bay in 2012. The red ship can be identified on the bottom of the photo for scale. }
\end{center}
\label{fig:Spread_area}
\end{figure}
 \clearpage

(a) Hexagonal elements are initialized in a staggered lattice as shown. Adjacent elements are bonded together. The element bonds (plotted in pink) form equilateral triangles which give the larger structure rigidity. The black circles show the circular element shape used in element interactions, and are inscribed inside the hexagonal shape used for mass-spreading. (b) Intersection of a hexagonal element and the ocean grid. The colors indicate the fraction of the hexagon that lies in each grid cell. These fractions are used as weights to spread LTIM properties to the ocean grid (see text for more details).

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/snapshots_ALE_z_Collapse_spread_area.png}
\caption{ {Snapshots of the fraction of ice cover in the LTIM tabular iceberg calving simulation. Snapshots are taken (a) 7, (b) 15, and (c) 30 days after calving. The dashed line in panel (c) shows the location of the vertical transects shown in Figures \ref{fig:Velocity_section_Collapse} and \ref{fig:Temperature_section_Collapse}}.}
\end{center}
\label{fig:Hex_intersections}
\end{figure}
 \clearpage

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/hex_intersecting_rectangles}
%\caption{ {(a) Hexagonal elements are initialized in a staggered lattice as shown. Adjacent elements are bonded together. The element bonds (plotted in pink) form equilateral triangles which give the larger structure rigidity. The black circles show the circular element shape used in element interactions, and are inscribed inside the hexagonal shape used for mass-spreading. (b) Intersection of a hexagonal element and the ocean grid. The colors indicate the fraction of the hexagon that lies in each grid cell. These fractions are used as weights to spread LTIM properties to the ocean grid (see text for more details).}}
%\end{center}
%\label{fig:Hex_intersections}
%\end{figure}
 %\clearpage

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supporting Information
%% (Optional) See AGUSuppInfoSamp.tex/pdf for requirements 
%% for Supporting Information.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

More Information and Advice:

%% ------------------------------------------------------------------------ %%
%
%  SECTION HEADS
%
%% ------------------------------------------------------------------------ %%

% Capitalize the first letter of each word (except for
% prepositions, conjunctions, and articles that are
% three or fewer letters).

% AGU follows standard outline style; therefore, there cannot be a section 1 without
% a section 2, or a section 2.3.1 without a section 2.3.2.
% Please make sure your section numbers are balanced.
% ---------------
% Level 1 head
%
% Use the \section{} command to identify level 1 heads;
% type the appropriate head wording between the curly
% brackets, as shown below.
%
%An example:
%\section{Level 1 Head: Introduction}
%
% ---------------
% Level 2 head
%
% Use the \subsection{} command to identify level 2 heads.
%An example:
%\subsection{Level 2 Head}
%
% ---------------
% Level 3 head
%
% Use the \subsubsection{} command to identify level 3 heads
%An example:
%\subsubsection{Level 3 Head}
%
%---------------
% Level 4 head
%
% Use the \subsubsubsection{} command to identify level 3 heads
% An example:
%\subsubsubsection{Level 4 Head} An example.
%
%% ------------------------------------------------------------------------ %%
%
%  IN-TEXT LISTS
%
%% ------------------------------------------------------------------------ %%
%
% Do not use bulleted lists; enumerated lists are okay.
% \begin{enumerate}
% \item
% \item
% \item
% \end{enumerate}
%
%% ------------------------------------------------------------------------ %%
%
%  EQUATIONS
%
%% ------------------------------------------------------------------------ %%

% Single-line equations are centered.
% Equation arrays will appear left-aligned.

Math coded inside display math mode \[ ...\]
 will not be numbered, e.g.,:
 \[ x^2=y^2 + z^2\]

 Math coded inside \begin{equation} and \end{equation} will
 be automatically numbered, e.g.,:
 \begin{equation}
 x^2=y^2 + z^2
 \end{equation}

% To create multiline equations, use the
% \begin{eqnarray} and \end{eqnarray} environment
% as demonstrated below.
\begin{eqnarray}
  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
        && + (y - y_{0}) \sin \Theta  \nonumber \\
  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
        && + (y - y_{0}) \cos \Theta.
\end{eqnarray}

%If you don't want an equation number, use the star form:
%\begin{eqnarray*}...\end{eqnarray*}

% Break each line at a sign of operation
% (+, -, etc.) if possible, with the sign of operation
% on the new line.

% Indent second and subsequent lines to align with
% the first character following the equal sign on the
% first line.

% Use an \hspace{} command to insert horizontal space
% into your equation if necessary. Place an appropriate
% unit of measure between the curly braces, e.g.
% \hspace{1in}; you may have to experiment to achieve
% the correct amount of space.

%% ------------------------------------------------------------------------ %%
%
%  EQUATION NUMBERING: COUNTER
%
%% ------------------------------------------------------------------------ %%

% You may change equation numbering by resetting
% the equation counter or by explicitly numbering
% an equation.

% To explicitly number an equation, type \eqnum{}
% (with the desired number between the brackets)
% after the \begin{equation} or \begin{eqnarray}
% command.  The \eqnum{} command will affect only
% the equation it appears with; LaTeX will number
% any equations appearing later in the manuscript
% according to the equation counter.
%

% If you have a multiline equation that needs only
% one equation number, use a \nonumber command in
% front of the double backslashes (\\) as shown in
% the multiline equation above.

% If you are using line numbers, remember to surround
% equations with \begin{linenomath*}...\end{linenomath*}

%  To add line numbers to lines in equations:
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}
